Model Checking Differentially Private Properties

### 2018-04-25 examples.tex
add mdp for above threshold

>>>>

\begin{figure}
  \centering
    \resizebox{\columnwidth}{!}{
    \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node
      distance=2cm,node/.style={circle,draw}]
      \node[node] (t0r1) at (-4.75, 0) { $t_0r_1$ };

      \draw (-3.95, 2.1) rectangle (-.05, 4.9);
      \node at (-3.25, 4.5) { $\vdots $};
      \node[node] (t'0r1) at (-3.25, 3.5) { $t'_0r_1$ };
      \node at (-3.25, 2.7) { $\vdots $};
      \draw (-3.95, -1.9) rectangle (-.05, 1.9);
      \node[node] (t'1r0) at (-3.25, 1.2) { $t'_1r_0$ };
      \node[node] (t'1r1) at (-3.25, 0) { $t'_1r_1$ };
      \node[node] (t'1r2) at (-3.25, -1.2) { $t'_1r_2$ };
      \node at (-1.95, 0) { $\cdots$ };
      \node at (-1.95, -1.2) { $\cdots$ };
      \draw (-3.95, -2.1) rectangle (-.05, -4.9);
      \node at (-3.25, -2.5) { $\vdots$ };
      \node[node] (t'2r1) at (-3.25, -3.5) { $t'_2r_1$ };
      \node at (-3.25, -4.3) { $\vdots$ };

      \node[node] (t'1r'0) at (-.75, 1.2) { $t'_1r'_0$ };
      \node[node] (t'1r'1) at (-.75, 0) { $t'_1r'_1$ };
      \node[node] (t'1r'2) at (-.75, -1.2) { $t'_1r'_2$ };

      \node[node] (tt0rr0) at (4.75, 1.2) { $\underline{t}_0\underline{r}_0$ };

      \draw (3.95, 2.1) rectangle (.05, 4.9);
      \node[node] (tt'0rr0) at (3.25, 4.2) { $\underline{t}'_0\underline{r}_0$ };
      \node at (3.25, 3) { $\vdots$ };
      \draw (3.95, -.9) rectangle (.05, 1.9);
      \node[node] (tt'1rr0) at (3.25, 1.2) { $\underline{t}'_1\underline{r}_0$ };
      \node at (3.25, 0) { $\vdots$ };

      \draw (3.95, -1.1) rectangle (.05, -4.9);
      \node[node] (tt'2rr0) at (3.25, -1.8) { $\underline{t}'_2\underline{r}_0$ };
      \node[node] (tt'2rr1) at (3.25, -3.0) { $\underline{t}'_2\underline{r}_1$ };
      \node[node] (tt'2rr2) at (3.25, -4.2) { $\underline{t}'_2\underline{r}_2$ };

      \node at (1.95, -4.2) { $\cdots$ };

      \node[node] (tt'2rr'0) at (.75, -1.8) { $\underline{t}'_2\underline{r}'_0$ };
      \node[node] (tt'2rr'1) at (.75, -3.0) { $\underline{t}'_2\underline{r}'_1$ };
      \node[node] (tt'2rr'2) at (.75, -4.2) { $\underline{t}'_2\underline{r}'_2$ };

      \path
      (t0r1) edge [bend left=20] node [above] { $\frac{1}{1}$ } (t'0r1)
      (t0r1) edge node [above] { $\frac{1}{1}$ } (t'1r1)
      (t0r1) edge [bend right=20] node [below] { $\frac{1}{1}$ } (t'2r1)

%      (t'1r1) edge node [above] { $\frac{1}{1}$ } (t'1r'0)
%      (t'1r1) edge node [above] { $\frac{1}{1}$ } (t'1r'1)
%      (t'1r1) edge node [above] { $\frac{1}{1}$ } (t'1r'2)

      (t'1r'0) edge [double] node [above] { $0|0, 0|1$ } (t'1r0)
      (t'1r'0) edge [double, bend left=10] node [above] 
              { $1|0, 1|1, 1|2$ } (t'1r1)
      (t'1r'0) edge [double, bend left=20] node [below] 
              { $2|1, 2|2$ } (t'1r2)

      (tt0rr0) edge [bend right=20] node [above] { $\frac{1}{1}$ } (tt'0rr0)
      (tt0rr0) edge node [above] { $\frac{1}{1}$ } (tt'1rr0)
      (tt0rr0) edge [bend left=20] node [below] { $\frac{1}{1}$ } (tt'2rr0)

      (tt'2rr'0) edge [double] node [above] { $0|0, 1|0$ } (tt'2rr0)
      (tt'2rr'0) edge [double] node [above] { $0|1, 1|1, 2|1$ } (tt'2rr1)
      (tt'2rr'0) edge [double] node [above] { $1|2, 2|2$ } (tt'2rr2)

      (tt'2rr'1) edge [double] node [above] { $0|0, 1|0$ } (tt'2rr0)
      (tt'2rr'1) edge [double] node [above] { $0|1, 1|1, 2|1$ } (tt'2rr1)
      (tt'2rr'1) edge [double] node [above] { $1|2, 2|2$ } (tt'2rr2)

      ;
      \end{tikzpicture}
    }
  \caption{Markov Decision Process for Above Threshold}
  \label{figure:mdp-above-threshold}
\end{figure}
